Evaluating urban greening scenarios for urban heat mitigation: a spatially-explicit approach

### 2020-11-09 reports/article-iop.tex
added IOP article latex source

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in,marginparwidth=2in]{geometry}

% use Unicode characters - try changing the option if you run into troubles with special characters (e.g. umlauts)
\usepackage[utf8]{inputenc}

% clean citations
\usepackage{cite}

@@

% line numbers
\usepackage[right]{lineno}

% improves typesetting in LaTeX
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% text layout - change as needed
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Remove % for double line spacing
%\usepackage{setspace} 
%\doublespacing

% use adjustwidth environment to exceed text width (see examples in text)
\usepackage{changepage}

% adjust caption style
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,singlelinecheck=off]{caption}

% remove brackets from references
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% headrule, footrule and page numbers
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}

% use \textcolor{color}{text} for colored text (e.g. highlight to-do areas)
\usepackage{color}

% define custom colors (this one is for figure captions)
\definecolor{Gray}{gray}{.25}

@@

% use if you want to put caption to the side of the figure - see example in text
\usepackage{sidecap}

% use for have text wrap around figures
\usepackage{wrapfig}
\usepackage[pscoord]{eso-pic}
\usepackage[fulladjust]{marginnote}
\reversemarginpar

@@

% math utils
\usepackage{amsmath}

% % citation aliases
% \usepackage{natbib}
% % https://tex.stackexchange.com/questions/323868/setting-two-different-aliases-name-2016-name-2016-with-defcitealias
% \newcommand{\mycitet}[1]{\citetalias{#1} (\citeyear{#1})}
% \newcommand{\mycitep}[1]{(\citetalias{#1} \citeyear{#1})}

% force floats in sections
\usepackage{float}

% \usepackage{caption}

% document begins here
\begin{document}
\vspace*{0.35in}

% \defcitealias{arezh2018bodenbedeckung}{ARE}
% \defcitealias{asitvd2018structure}{ASIT VD}
% \defcitealias{bve2019mopube}{BVE}

% title goes here:
\begin{flushleft}
  {
    % \Large Spatially-explicit simulation of urban heat mitigation by increasing the tree canopy cover
    % \Large Targeted urban greening strategies for urban heat mitigation: a spatially-explicit approach
    \Large Evaluating urban greening scenarios for urban heat mitigation: a spatially-explicit approach
    \textbf\newline{}
  }
  \newline
  % authors go here:
  \\
  Mart\'i Bosch\textsuperscript{1,*},
  Maxence Locatelli\textsuperscript{1},
  Perrine Hamel\textsuperscript{2},
  R\'emi Jaligot\textsuperscript{1},
  J\'er\^ome Chenal\textsuperscript{1},
  St\'ephane Joost\textsuperscript{3,1}
  \\
  \bigskip
  \bf{1} Urban and Regional Planning Community, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
  \\ 
  \bf{2} Asian School of the Environment, Nanyang Technological University, Singapore
  \\
  \bf{3} Laboratory of Geographic Information Systems, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland
  \\
  \bigskip
  \bf{*} Corresponding author: marti.bosch@epfl.ch

\end{flushleft}

\section*{Abstract}

% Urban green space, especially trees, can contribute to the reduction of urban temperatures in extreme heat events.
Urban green infrastructure, especially trees, are widely regarded as one of the most effective ways to reducing urban temperatures in extreme heat events, and alleviate its adverse impacts on human health and well-being.
% Nevertheless, the effect of the spatial pattern on urban temperatures.
Nevertheless, urban planners and decision-makers are still lacking methods and tools to spatially evaluate the cooling effects of urban green spaces and exploit them to assess greening strategies at the urban agglomeration scale.
This article introduces a novel spatially-explicit approach to simulate urban greening scenarios by increasing the tree canopy cover in the existing urban fabric, and evaluating their heat mitigation potential.
The latter is achieved by applying the InVEST urban cooling model to the synthetic land use/land cover maps generated for the greening scenarios.
% A case study in the urban agglomeration of Lausanne, Switzerland, experiments with a range of tree canopy increases in distinct spatial configurations, and shows a potential alleviation of the urban nighttime temperatures of up to 2$\degree$C.
A case study in the urban agglomeration of Lausanne, Switzerland, illustrates the development of tree canopy scenarios following distinct spatial distribution strategies.
The spatial pattern of the tree canopy strongly influences the human exposure to the highest temperatures, and small increases in the abundance of tree canopy cover with the appropriate spatial configuration can have major impacts on human health and well-being.
% This article
The proposed approach supports urban planning and the design of nature-based solutions to enhance climate resilience.

% now start line numbers
\linenumbers

% the * after section prevents numbering
\section*{Introduction}

@@

Urbanization is a global phenomenon that increasingly concentrates the world's population in urban areas, with the latter expected to grow in both the number of dwellers and spatial extent over the next decades \cite{seto2011meta, angel2012atlas, unitednations2018world}.
As a major force of landscape change, urbanization is characterized by the conversion of natural to artificial surfaces, which alters the energy and water exchanges as well as the movement of air. Such changes often result in the urban heat island (UHI) effect, a phenomenon by which urban temperatures are warmer than its rural surroundings \cite{oke1973city,oke1982energetic,arnfield2003two,voogt2003thermal,grimmond2007urbanization,phelan2015urban}. % \cite{oke1982energetic}. 
% The negative impacts of UHI have been widely documented and include increased water and energy consumption \cite{santamouris2015impact}, reduced productivity \cite{kjellstrom2009workplace} and increased health risks \cite{kovats2008heat,laaidi2012impact}.
The negative impacts of UHI have been widely documented and include increased energy and water consumption \cite{akbari2001cool,golden2006energy,santamouris2015impact}, reduced workplace productivity \cite{kjellstrom2009workplace,zander2015heat} and aggravation of health risks \cite{chestnut1998analysis,kovats2008heat,laaidi2012impact}.
% As urban areas grow and global temperatures increase, heat waves are expected to become more intense and frequent ant the UHI effect
As urban areas grow and global temperatures rise, the UHI effect is expected to become more intense \cite{meehl2004more,huang2019projecting}, which makes urban heat mitigation a major priority for urban planning and policy-making \cite{geneletti2020planning}.
% Green infrastructure

% To that end, cities are increasingly
Increasing urban green space, especially the urban tree canopy, has been one of the most widely advocated strategies of urban heat mitigation. Nevertheless, the impacts of the urban tree canopy on air temperature show a complex spatial behaviour that remains poorly understood \cite{bowler2010urban,phelan2015urban,koc2018evaluating}.
% Therefore, there is an urgent need to develop robust and spatially explicit methods to quantify the contribution of urban green space to urban heat mitigation \cite{haaland2015challenges,artmann2019urban}.
% Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain.
% TODO: While many case studies have reproted strong evidence of the heat mitigation of urban green space, e.g., cooling effects of parks, very few studies have attempted to model such effects in space so that synthetic scenarios can be evaluated
% TODO: from the ecosystem service perspective, there is a need to consider green space development for the entire urban region \cite{lin2013sharing,haaland2015challenges,artmann2019urban}
While many case studies have reported evidence of the cooling effects of urban green areas, the relationship between their size and their cooling capacity is non-linear \cite{zardo2017estimating}, and little is known about how the overall spatial configuration of urban green spaces affects the heat mitigation at the urban agglomeration scale \cite{lin2013sharing,jim2013sustainable,haaland2015challenges,artmann2019urban}.
% TODO: case studies might be hard to generalize, e.g., effects of the background climate \cite{zhou2017effects}, \cite{yu2018strong,wang2020significant}.
% Additionally, the effects configuration of urban green space on heat mitigation are strongly mediated by the background climate of the region of study \cite{zhou2017effects,yu2018strong,wang2020significant}.
% what is the gap that we are addressing: there have not been fine-grained evaluations of the effect of increasing the tree canopy in realistic settings.
Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain, largely because of the lack of fine-grained approaches to evaluate the cooling effects of the spatial pattern of the tree canopy at the urban agglomeration scale. % , which consider the existing urban fabric and local environmental context.

@@

With the aim of addressing the above shortcomings, the present work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
The proposed method consists of two major parts.

@@

Finally, the simulated temperature map is coupled with a gridded population census in order to evaluate the human exposure to urban heat in the scenario.

@@

With the aim of quantifying the effects of the abundance and spatial configuration of the tree canopy cover on urban heat mitigation, a set of synthetic scenarios are generated by increasing different proportions of tree canopy cover in distinct spatial configurations. % and human thermal comfort

@@

\section*{Materials and Methods}

\subsection*{Study area}

Lausanne is the fourth largest Swiss urban agglomeration with 420757 inhabitants as of January 2019 \cite{sfso2018city}. The agglomeration is located at the Swiss Plateau and on the shore of the Lake L\'eman, and is characterized by a continental temperate climate with mean annual temperatures of 10.9 $\degree$C and mean annual precipitation of 100 mm, with a dominating vegetation of mixed broadleaf forest. The spatial extent of the study has been selected following the recent application of the InVEST urban cooling model to Lausanne by Bosch et al. \cite{bosch2020spatially}, and covers an area of 112.46 $km^2$.

In order to evaluate the human exposure to UHI, the population data for the study area has been extracted from the population and households statistics (STATPOP) \cite{sfso2020statistique} provided at a 100~m resolution by the Swiss Federal Statistical Office (SFSO) with the Python library swisslandstats-geopy \cite{bosch2019swisslandstats}.

\subsection*{Simulation with the InVEST urban cooling model}

The spatial distribution of air temperatures is simulated with the InVEST urban cooling model (version 3.8.0) \cite{sharp2020invest}, which is based on the heat mitigation provided by shade, evapotranspiration and albedo.
The main inputs are a land use/land cover (LULC) raster map, a reference evapotranspiration raster and a biophysical table containing model information of each LULC class of the map.
% A detailed overview of the model can be found in its user guide \cite{sharp2020invest} as well as in Bosch et al. \cite{bosch2020spatially}.
% Each row of the biophysical table represents a LULC class, and features the following columns:
% \begin{itemize}
% \item \texttt{lucode} the LULC class code as represented in the LULC raster map
% \item \texttt{Shade} a value between 0 and 1 representing the proportion of tree canopy cover in such LULC class
% \item \texttt{Kc} the evapotranspiration coefficient
% \item \texttt{Albedo} a value between 0 and 1 representing the proportion of solar radiation directly reflected by the LULC class
% \item \texttt{Green\_area} whether the LULC class should be considered a green area
% % \item \texttt{Building\_intensity} a value between 0 and 1 representing the ratio between floor area and land area
% \end{itemize}
The LULC maps have been obtained by rasterizing the vector geometries of the official cadastral survey of the Canton of Vaud \cite{asitvd2018structure} as of August 2019 to a 10~m resolution. Such a dataset distinguishes 25 LULC classes which are relevant ot the urban, rural and wild landscapes encountered in Switzerland.
The reference evapotranspiration pixel values are estimated with the Hargreaves equation \cite{hargreaves1985reference} based on the daily minimum, average and maximum air temperature values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology (MeteoSwiss) \cite{frei2014interpolation}.
The biophysical table used in this study is shown in \autoref{tab:si-biophysical-table}.
A more thorough description of the model and the data inputs can be found in Bosch et al. \cite{bosch2020spatially}.

@@

The parameters of the model are set based on its calibration to the same study area in previous work \cite{bosch2020spatially}.
Finally, the rural reference temperature ($T_{ref}$) and UHI magnitude ($UHI_{max}$) values are derived from the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ is set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \cite{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ is set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

\subsection*{Refining LULC classes based on tree cover and building density}
\label{sec:refin-lulc-class}

% To better account for the spatial heterogeneity of cities, a procedure to redefine the LULC classes from the cadastral survey has been designed, which further distinguishes the LULC classes depending on their proportional cover of both trees and buildings. Such reclassification is based on combining the 10~m raster LULC map with two 1~m binary raster masks, one for the tree canopy raster and another for the buildings. % , and consists of three main steps.
A procedure to redefine the LULC classes from the cadastral survey has been designed to distinguish the LULC classes depending on their proportional cover of both trees and buildings. The reclassification is achieved by combining the 10~m raster LULC map with two 1~m binary raster masks, one for the tree canopy raster and another for the buildings. % , and consists of three main steps.
The 1~m binary tree canopy mask has been derived from the SWISSIMAGE orthomosaic \cite{swisstopo2019swissimage}, by means of the Python library DetecTree \cite{bosch2020detectree}, which implements the methods proposed by Yang et al. \cite{yang2009tree}. The estimated classification accuracy of the tree canopy classification is of 91.75\%. On the other hand, the 1~m binary building mask has been obtained by rasterizing the buildings of the vector cadastral survey \cite{asitvd2018structure}.

% The reclassification procedure consists of three steps.
% % First, for each LULC class, the set of 10m pixels of such class is coupled with the tree canopy and building masks
% Firstly, each 10~m pixel is coupled with the tree canopy and building masks in order to respectively compute its proportion of tree and building cover.
% % Secondly, each LULC class is further refined into a set of subclasses depending on the joint distribution of tree cover and building cover of its 10~m pixels, e.g., the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''. %  its set of 10~m pixels are % the 10m pixels of each LULC class are grouped into equally-spaced bins according to their proportion of tree cover
% Secondly, the set of 10~m pixels of each LULC class are grouped into a set of bins to form two histograms, one based on their proportion of tree cover and the other analogously for the building cover.
% % which groups the 10~m pixels of each LULC class into an increasing number of equally-spaced bins according to their proportion of tree cover, until adding an extra bin results in having a bin whose number of samples is lower than certain threshold.
% The number of bins is determined by means of an iterative procedure which distributes the 10~m pixels into an increasing number of equally-spaced bins until adding an extra bin results in having a bin whose number of samples is lower than certain threshold.
% After empirical exploration, a threshold value of 3~\% has been manually chosen with the aim of obtaining a set of refined LULC codes that can be interpreted easily.
% % cartesian product
% Finally, the two histograms are joined so that each LULC class is further refined into a set of subclasses, e.g., the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''.
The reclassification procedure consists of three steps.
Firstly, each 10~m pixel is coupled with the tree canopy and building masks in order to respectively compute its proportion of tree and building cover.
Secondly, the set of 10~m pixels of each LULC class are grouped into a user-defined set of bins to form two histograms, one based on their proportion of tree cover and the other analogously for the building cover.
% cartesian product
Lastly, the two histograms are joined so that each LULC class is further refined into a set of classes. For example, if two bins were used for both the tree and building cover, the ``sidewalk'' LULC code might be further refined into ``sidewalk with low tree/low building cover'', ``sidewalk with low tree/high building cover'', ``sidewalk with high tree/low building cover'' and ``sidewalk with high tree/high building cover''.

In the present work, four equally spaced bins (i.e., distinguishing 0-25\%, 25-50\%, 50-75\% and 75-100\% intervals) have been used to reclassify each LULC class according to both the tree and building cover.
Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.
Therefore, adjacent pixels with a tree canopy cover over 75\% can 
Finally, in order to adapt the biophysical table of the InVEST urban cooling model to the reclassified LULC classes, the shade coefficients are computed as the midpoint of the bin interval of each level of tree cover (i.e., 0.125, 0.375, 0.625 and 0.875), whereas the albedo coefficients have been linearly interpolated based on the level of building cover (see \autoref{tab:si-biophysical-table}).

% \subsubsection{Calibration and evaluation of the model}

% The urban cooling model is calibrated to the study area following the approach proposed by Bosch et al. \cite{bosch2020spatially}, which consists in employing a simulated annealing procedure to find the combination of cooling capacity weights $w_{S}$, $w_{AL}$ and $w_{ET}$, the distance over which green spaces have a cooling effect $d_{cool}$ and the air mixing radius $r$ that best-fit the air temperature measurements from monitoring stations.

% In the present work, the calibration is based on the measurements of the same monitoring stations and the same dates as Bosch et al. \cite{bosch2020spatially}, yet . The coefficient of determination of the calibrated model is $R^2 = 0.90$, with a mean absolute error of $MAE = 1.19 \degree C$ and root-mean-square error of $RMSE = 1.45 \degree C$.

% \subsection{Relationship between the spatial pattern of tree canopy on urban heat mitigation}

% In order to explore the relationships between the

% The OLS, diagnostics for spatial dependece and spatial regression are performed with the PySAL library (v2.3.0) \cite{rey2010pysal}, whereas the Pearson and partial correlation analysis are performed respectively with the SciPy (v1.5.2) \cite{virtanen2020scipy} and Pingouin (v0.3.7) \cite{vallat2018pingouin} libraries.

\subsection*{Generation of urban greening scenarios}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}

% \newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}

% % harvard citations
% \usepackage{harvard}

% citations
% \usepackage[maxbibnames=10,maxcitenames=2,backend=biber]{biblatex}
\usepackage[comma, authoryear]{natbib}
% https://tex.stackexchange.com/questions/323868/setting-two-different-aliases-name-2016-name-2016-with-defcitealias
\newcommand{\mycitep}[1]{(\citetalias{#1} \citeyear{#1})}

@@

@@

@@

\begin{document}

% citation aliases
\defcitealias{asitvd2018structure}{ASIT-VD}
\defcitealias{sfso2018city}{SFSO}
\defcitealias{sfso2020statistique}{SFSO}
\defcitealias{swisstopo2019swissimage}{SWISSTOPO}

\title[Urban greening scenarios for urban heat mitigation]{Evaluating urban greening scenarios for urban heat mitigation: a spatially-explicit approach}

\author{Mart\'i Bosch$^{1,*}$, Maxence Locatelli$^1$, Perrine Hamel$^2$, R\'emi Jaligot$^1$, J\'er\^ome Chenal$^1$, St\'ephane Joost$^{3,1}$}

\address{
  $^1$Urban and Regional Planning Community, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland \\
  $^2$Asian School of the Environment, Nanyang Technological University, Singapore \\
  $^3$Laboratory of Geographic Information Systems, \'Ecole Polytechnique F\'ed\'erale de Lausanne, Lausanne, Switzerland}
\ead{$^*$marti.bosch@epfl.ch}
% \vspace{10pt}
% \begin{indented}
% \item[]August 2017
% \end{indented}

\begin{abstract}
Urban green infrastructure, especially trees, are widely regarded as one of the most effective ways to reducing urban temperatures in extreme heat events, and alleviate its adverse impacts on human health and well-being.
Nevertheless, urban planners and decision-makers are still lacking methods and tools to spatially evaluate the cooling effects of urban green spaces and exploit them to assess greening strategies at the urban agglomeration scale.
This article introduces a novel spatially-explicit approach to simulate urban greening scenarios by increasing the tree canopy cover in the existing urban fabric, and evaluating their heat mitigation potential.
The latter is achieved by applying the InVEST urban cooling model to the synthetic land use/land cover maps generated for the greening scenarios.
A case study in the urban agglomeration of Lausanne, Switzerland, illustrates the development of tree canopy scenarios following distinct spatial distribution strategies.
The spatial pattern of the tree canopy strongly influences the human exposure to the highest temperatures, and small increases in the abundance of tree canopy cover with the appropriate spatial configuration can have major impacts on human health and well-being.
The proposed approach supports urban planning and the design of nature-based solutions to enhance climate resilience.
\end{abstract}

%
% Uncomment for keywords
\vspace{2pc}
\noindent{\it Keywords}: urban heat island, green infrastructure, mitigation, spatial planning
%
% Uncomment for Submitted to journal title message
\submitto{\ERL}
%
% Uncomment if a separate title page is required
%\maketitle
% 
% For two-column output uncomment the next line and choose [10pt] rather than [12pt] in the \documentclass declaration
%\ioptwocol
%

\section{Introduction}

@@

Urbanization is a global phenomenon that increasingly concentrates the world's population in urban areas, with the latter expected to grow in both the number of dwellers and spatial extent over the next decades \citep{seto2011meta,angel2012atlas,unitednations2018world}.
As a major force of landscape change, urbanization is characterized by the conversion of natural to artificial surfaces, which alters the energy and water exchanges as well as the movement of air. Such changes often result in the urban heat island (UHI) effect, a phenomenon by which urban temperatures are warmer than its rural surroundings \citep{oke1973city,oke1982energetic,arnfield2003two,voogt2003thermal,grimmond2007urbanization,phelan2015urban}. % \cite{oke1982energetic}. 
% The negative impacts of UHI have been widely documented and include increased water and energy consumption \cite{santamouris2015impact}, reduced productivity \cite{kjellstrom2009workplace} and increased health risks \cite{kovats2008heat,laaidi2012impact}.
The negative impacts of UHI have been widely documented and include increased energy and water consumption \citep{akbari2001cool,golden2006energy,santamouris2015impact}, reduced workplace productivity \citep{kjellstrom2009workplace,zander2015heat} and aggravation of health risks \citep{chestnut1998analysis,kovats2008heat,laaidi2012impact}.
% As urban areas grow and global temperatures increase, heat waves are expected to become more intense and frequent ant the UHI effect
As urban areas grow and global temperatures rise, the UHI effect is expected to become more intense \citep{meehl2004more,huang2019projecting}, which makes urban heat mitigation a major priority for urban planning and policy-making \citep{geneletti2020planning}.
% Green infrastructure

% To that end, cities are increasingly
Increasing urban green space, especially the urban tree canopy, has been one of the most widely advocated strategies of urban heat mitigation. Nevertheless, the impacts of the urban tree canopy on air temperature show a complex spatial behaviour that remains poorly understood \citep{bowler2010urban,phelan2015urban,koc2018evaluating}.
% Therefore, there is an urgent need to develop robust and spatially explicit methods to quantify the contribution of urban green space to urban heat mitigation \cite{haaland2015challenges,artmann2019urban}.
% Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain.
% TODO: While many case studies have reproted strong evidence of the heat mitigation of urban green space, e.g., cooling effects of parks, very few studies have attempted to model such effects in space so that synthetic scenarios can be evaluated
% TODO: from the ecosystem service perspective, there is a need to consider green space development for the entire urban region \cite{lin2013sharing,haaland2015challenges,artmann2019urban}
While many case studies have reported evidence of the cooling effects of urban green areas, the relationship between their size and their cooling capacity is non-linear \citep{zardo2017estimating}, and little is known about how the overall spatial configuration of urban green spaces affects the heat mitigation at the urban agglomeration scale \citep{lin2013sharing,jim2013sustainable,haaland2015challenges,artmann2019urban}.
% TODO: case studies might be hard to generalize, e.g., effects of the background climate \cite{zhou2017effects}, \cite{yu2018strong,wang2020significant}.
% Additionally, the effects configuration of urban green space on heat mitigation are strongly mediated by the background climate of the region of study \cite{zhou2017effects,yu2018strong,wang2020significant}.
% what is the gap that we are addressing: there have not been fine-grained evaluations of the effect of increasing the tree canopy in realistic settings.
Therefore, the extent to which cities can use green infrastructure to reduce heat stress remains uncertain, largely because of the lack of fine-grained approaches to evaluate the cooling effects of the spatial pattern of the tree canopy at the urban agglomeration scale. % , which consider the existing urban fabric and local environmental context.

@@

With the aim of addressing the above shortcomings, this work introduces a novel spatially-explicit method to evaluate the heat mitigation potential of altering the abundance and spatial configuration of the urban tree canopy cover in realistic settings.
The proposed method consists of three major parts.

@@

Finally, the simulated temperature map is coupled with a gridded population census to evaluate the human exposure to urban heat in the scenario.

@@

% In order to quantify the effects of the abundance and spatial configuration of the tree canopy cover on urban heat mitigation, a set of synthetic scenarios are generated by increasing different proportions of tree canopy cover in distinct spatial configurations. % and human thermal comfort
To that end, a set of synthetic scenarios are generated by increasing different proportions of tree canopy in distinct spatial configurations, which allow evaluating the abundance and configuration effects of the tree canopy on urban heat mitigation.

@@

\section{Materials and Methods}

\subsection{Study area}

Lausanne is the fourth largest Swiss urban agglomeration with 420757 inhabitants as of January 2019 \mycitep{sfso2018city}. The agglomeration is located at the Swiss Plateau and on the shore of the Lake L\'eman, and is characterized by a continental temperate climate with mean annual temperatures of 10.9 $\degree$C and mean annual precipitation of 100 mm, with a dominating vegetation of mixed broadleaf forest.
The spatial extent of the study has been selected following the recent application of the InVEST urban cooling model to Lausanne by \cite{bosch2020spatially}, and covers an area of 112.46 $km^2$.

To evaluate the human exposure to UHI, the population data for the study area has been extracted from the population and households statistics (STATPOP) \mycitep{sfso2020statistique} provided at a 100~m resolution by the Swiss Federal Statistical Office with the swisslandstats-geopy library \citep{bosch2019swisslandstats}.

\subsection{Simulation with the InVEST urban cooling model}

The spatial distribution of air temperature is simulated with the InVEST urban cooling model, version 3.8.0 \citep{sharp2020invest}, which is based on the heat mitigation provided by shade, evapotranspiration and albedo.
The main inputs are a land use/land cover (LULC) raster map, a reference evapotranspiration raster and a biophysical table containing model information of each LULC class of the map.
% A detailed overview of the model can be found in its user guide \cite{sharp2020invest} as well as in Bosch et al. \cite{bosch2020spatially}.
% Each row of the biophysical table represents a LULC class, and features the following columns:
% \begin{itemize}
% \item \texttt{lucode} the LULC class code as represented in the LULC raster map
% \item \texttt{Shade} a value between 0 and 1 representing the proportion of tree canopy cover in such LULC class
% \item \texttt{Kc} the evapotranspiration coefficient
% \item \texttt{Albedo} a value between 0 and 1 representing the proportion of solar radiation directly reflected by the LULC class
% \item \texttt{Green\_area} whether the LULC class should be considered a green area
% % \item \texttt{Building\_intensity} a value between 0 and 1 representing the ratio between floor area and land area
% \end{itemize}
% The LULC maps have been obtained by rasterizing the vector geometries of the official cadastral survey of the Canton of Vaud \mycitep{asitvd2018structure} as of August 2019 to a 10~m resolution. Such a dataset distinguishes 25 LULC classes which are relevant ot the urban, rural and wild landscapes encountered in Switzerland.
The LULC maps have been obtained by rasterizing the official cadastral survey of the Canton of Vaud \mycitep{asitvd2018structure} as of August 2019 to a 10~m resolution. Such a dataset distinguishes 25 LULC classes which are relevant ot the urban, rural and wild landscapes encountered in Switzerland.
The reference evapotranspiration pixel values are estimated with the Hargreaves equation \citep{hargreaves1985reference} based on the daily minimum, average and maximum air temperature values of the 1~km gridded inventory of by the Federal Office of Meteorology and Climatology \citep{frei2014interpolation}.
The biophysical table used in this study is shown in \autoref{tab:si-biophysical-table}.
A more thorough description of the model and the data inputs can be found in \cite{bosch2020spatially}.

@@

The parameters of the model are set based on its calibration to the same study area in previous work \citep{bosch2020spatially}.
Finally, the rural reference temperature ($T_{ref}$) and UHI magnitude ($UHI_{max}$) values are derived from the air temperature of 11 monitoring stations in the study area (see \autoref{fig:monitoring-stations}). More precisely, $T_{ref}$ is set as the 9 p.m. air temperature measurement --- the moment of maximal UHI intensity in Switzerland \citep{burgst2019representing} --- of the station showing the lowest temperature value, and $UHI_{max}$ is set as the difference between the 9 p.m. temperature measurement of the station showing the highest temperature value and $T_{ref}$.
% Given that the UHI effect in Switzerland reaches its maximal intensity around 9 p.m. \cite{burgst2019representing}, this study evaluates it based on the air temperature observations of that hour.
With the above definitions, a reference day for the simulations has been selected from the 2018-2019 period as the day showing the maximum $UHI_{max}$ with $T_{ref} > 20$. Such a date corresponds to July 27$^{th}$ 2018, with $T_{ref} = 20.60 \degree C$ and $UHI_{max} = 7.38 \degree C$.

\subsection{Refining LULC classes based on tree cover and building density}
\label{sec:refin-lulc-class}

% To better account for the spatial heterogeneity of cities, a procedure to redefine the LULC classes from the cadastral survey has been designed, which further distinguishes the LULC classes depending on their proportional cover of both trees and buildings. Such reclassification is based on combining the 10~m raster LULC map with two 1~m binary raster masks, one for the tree canopy raster and another for the buildings. % , and consists of three main steps.
A procedure to redefine the LULC classes from the cadastral survey has been designed to distinguish the LULC classes depending on their proportional cover of both trees and buildings. The reclassification is achieved by combining the 10~m raster LULC map with two 1~m binary raster masks, one for the tree canopy raster and another for the buildings. % , and consists of three main steps.
The 1~m tree canopy mask is derived from the SWISSIMAGE orthomosaic \mycitep{swisstopo2019swissimage}, by means of the DetecTree library \citep{bosch2020detectree}, which implements the methods of \cite{yang2009tree}. The estimated accuracy of the tree canopy classification is of 91.75\%.
% On the other hand, the 1~m binary building mask has been obtained by rasterizing the buildings of the vector cadastral survey \citep{asitvd2018structure}.
The 1~m building mask is obtained by rasterizing the buildings of the vector cadastral survey \mycitep{asitvd2018structure}.

\subsection{Generation of urban greening scenarios}

Starting from the refined LULC map, a set of urban greening scenarios are generated by altering the LULC classes of certain candidate pixels in a way that corresponds to reasonable transformations that could occcur in urban areas.
More precisely, pixels whose base LULC class corresponds to ``building'', ``road, path'', ``sidewalk'', ``traffic island'', ``other impervious'' and ``garden'' are changed to the LULC code that has the same base class but with the highest tree cover, e.g.,  pixels of a post-refinement class ``sidewalk with low tree/low building cover'' are be changed to ``sidewalk with high tree/low building cover''.
% limit such that the proportion of tree canopy cover and the proportion of building cover (i.e., "shade" + "bulding_intensity") does not amount to more than 100\%
To ensure that such an increase of the tree canopy cover is performed only where the existing urban fabric permits it, pixels might only be transformed when two conditions are met.
% First, the transformations might only take place in pixels where the proportion of building cover is under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
First, the proportion of building cover in the candidate pixels must be under 25\%, i.e., there is a 75\% of the pixel area which could be occupied by a tree crown.
% \footnote{Following the advice given by the directorate of resoures and natural heritage in the Canton of Vaud (DGE-DIRNA), the threshold over which a pixel is considered to have a high tree canopy cover has been set to 75\%, which corresponds to placing trees of a spheric crown with a 5~m radius spaced 10~m from one another so that they form a continuous canopy.}
Secondly, pixels of the ``road, path'' class might only be transformed when they are adjacent to a pixel of a different class, which prevents increasing the tree canopy cover in pixels that are in the middle of a road (e.g., a highway).
